\documentclass{article}
\usepackage[utf8]{inputenc}
\setlength{\parindent}{0pt} 

\newcommand{\SubItem}[1]{
    {\setlength\itemindent{15pt} \item[] #1}
}

\title{Constitution}
\author{Data Science @ UCSC}

\begin{document}

\maketitle
\tableofcontents

\newpage

\section{Name and Purpose}

\subsection{Name}
\begin{itemize}
    \item[1.] This organization shall be called Data Science at University of California, Santa Cruz, herein referred to as Data Science @ UCSC.
    \item[2.]  The organization may officially be referred to by any of the following terms:
    \SubItem{} (a) Data Science @ UCSC.
    \SubItem{} (b) Data Science at University of California, Santa Cruz.
    \SubItem{} (b) Data Science at UC Santa Cruz.
    \SubItem{} (d) DS @ UCSC.
    \item[]
\end{itemize}

\subsection{Purpose}
\begin{itemize}
    \item[1.] Data Science @ UCSC seeks to promote interest in Data Science
    while prepearing students for future work through group projects, educational workshops and industry events.
    \item[2.] Data Science @ UCSC helps students develop a passion for applying data science to solving real world problems and gaining insights.
    \item[3.] Data Science @ UCSC aspires to create a inclusive environment where students interested data science will network and grow.
\end{itemize}


\section{Statement of Responsibility}

The Authorized Representatives, Officers and Members of this organization:
\begin{itemize}
    \item[1.] Accept responsibility for compliance with University policies and campus regulations.
    \item[2.] Understand and agree to abide by the provisions of the anti-hazing statues in the California Education Code or Penal Code (as amended, effective January 1st, 2007).
    \item[3.] Affirm that the rules, regulations and policies of the University of California and UCSC shall supersede the rules, regulations, policies and/or bylaws of this organization 
 
\end{itemize}


\section{Membership}

\subsection{Eligibility}
\begin{itemize}
    \item[1.] Membership in DSS at UCSC shall be open to all students at the University of California, Santa Cruz.
    \item[2.] Membership shall not be restricted according to race, creed, age, gender, 
    disability, nationality, sexual orientation, economic status, veterean status or parenthood.
    \item[3.] Non-students are welcome to participate in activities but may nor be members,
    hold officer positions, or vote.  
\end{itemize} 


\subsection{Classifications}
\begin{itemize}
    \item[1.] Member: Students, Staff of Faculty who completed registration of Data Science @ UCSC
    \item[2.] Active Member: Members who attend at least 2 meetings or events in the current quarter
    \item[3.] Alumni Member: Members who are no longer affiliated with UCSC, members automatically become alumni upon leaving the University. 
\end{itemize}

\subsection{Termination}
\begin{itemize}
    \item[1.] Membership in Data Science @ UCSC can be resigned at any time upon notifying the 
    President or Vice-President.
    \item[2.] Membership may be revoked from any member demonstrating behavior that is a 
    substantial  violation of the Data Science @ UCSC Code of Conduct, University policies or campus  regulations upon a majority (>50\%)affirmative vote of Board of Officers.
    The result of this vote will be delivered through official organization communication 
    channels  (email or messaging workspace)
    \item[3.] When membership is resigned or revoked, the member shall lose
    access to any organization software (e.g. code repositories, communication platforms).    
\end{itemize}


\section{Officers}

\subsection{Eligibility}
\begin{itemize}
    \item[1.] Any Active Member who has been part of the organization
    for at least one quarter is eligible to become an Officer.
\end{itemize}

\subsection{Board of Officers}
\begin{itemize}
    \item[1.] The Board of Offficers consists of all current Officers.
    \item[2.] The Board of Officers shall meet at the beginning of each quarter to plan 
    future events. 
\end{itemize}

\subsection{Duties and Responsabilities}
\begin{itemize}
    \item[1.] President:
        \SubItem{(a)} Facilitate all organization meetings.
        \SubItem{(b)} Represent the organization.
        \SubItem{(c)} Ensure the continuing registration of the organization with SOMeCA.
    \item[] % blank item to fix indentation bug
    \item[2.] Vice-President
        \SubItem{(a)} Assist the President in all of his duties.
        \SubItem{(b)} Manage organization communications and social media outreach.
    \item[] % blank item to fix indentation bug
    \item[3.] Webmaster:
        \SubItem{(a)} Manage the organization's website. 
        \SubItem{(b)} Add information and features to the organization's website at the 
        direction of the Board of Officers.
    \item[] % blank item to fix indentation bug
    \item[4.] Treasurer: 
        \SubItem{(a)} Keep records of income and expenses. 
        \SubItem{(b)} Make regular financial reports.
        \SubItem{(c)} Expend funds at the direction of the Board of Officers .
    \item[] % blank item to fix indentation bug
    \item[5.] Other Officers:
        \SubItem{(a)} Facilitate organization meetings.
        \SubItem{(a)} Spearhead at least one meeting or activity in the quarter.
\end{itemize}

\subsection{Nomination and Removal}
\begin{itemize}
    \item[1.] New Officers are selected at the end of the academic year, or 
    whenever there is a vacant position to fill 
        \SubItem{(a)} The Board of Officers must notify members of vacant positions 
        within a week. 
    \item[2.] Any member who has been active for at least an academic quarter is eligible to 
    become an Officer.
    \item[3.] Members who desire so can apply to become an Officer by notifying any current 
    Officer of their interest.  
    \item[4.] Candidates shall be interviewed by at least two current Officers within two 
    weeks of their application. The interview should examine the candidates' adherance  
    to the mission of DSS at UCSC, ability to match the time commitment that comes with 
    the responsabilities of the position, and knowledge of relevant topics in data science.
    \item[5.] Final decisions on candidate Officers shall be reached by a two-thirds majority 
    vote of the Board of Officers.
    \item[6.] Officers shall serve for the current academic year from time of election.
    \item[7.] Officer may be revoked upon a two-thirds affirmative vote of the Board of 
    Officers for failing to perform duties or demonstrating behavior 
    that is a substantial violation of the Data Science @ UCSC Code of Conduct,
     University policies or campus regulations.
        \SubItem{(a)} Such violations may be reported to the President or Vice-President
    \item[8.] Officers may resign at any time upon notifying the President or Vice-President.
        \SubItem{(a)} If the President, Vice-President, Webmaster or Treasurer resign, the Board of Officers shall elect a new Officer to fill the vacated position.  
    \item[9.] % blank item to fix indentation bug
    \item[10.] At the end of the academic year, the Board of Officers shall elect a new 
    President and Vice-President to serve for the following academic year. 
        \SubItem{(a)}  Upon election of a new President or Vice-President, the current 
        President and Vice-President shall transfer all relevant organization documents, 
        social media logins, and access permissions. 
\end{itemize}

\section{Organization Decision-Making}
\begin{itemize}
    \item[1.] Voting privileges shall be granted to the Board of Officers.
    \item[2.] Votes may only occur with a minimum of two-thirds of Officers present 
    \item[2.] Decisions shall be reached by simple majority ($>50\%$) vote unless otherwise 
    specified in this Constitution.    
    \item[3.] In the event that a member disagrees with the a decision reached by the  
    Board of Officers, the member may request a general vote on the issue 
        \SubItem{(a)} In order for the request for a general vote to be approved, 
        at least three Members must notify the Board of Officers with their disagreements.
        \SubItem{(b)} General votes shall take place with at least $50\%$ of Active Members 
        present.
        \SubItem{(c)} Decisions shall be reached by a simple majority ($>50\%$) vote. 
\end{itemize}


\section{Financial Records}

\begin{itemize}
    \item[1.] Financial records shall be kept by the Treasurer.
    \item[2.] The Treasurer shall produce new financial reports:
        \SubItem{(a)} At the end of each quarter.
        \SubItem{(b)} After each financial transaction.   
    \item[3.] The Treasurer shall grant viewing access of financial records upon 
    the request of any Active Member   
\end{itemize}


\section{Amendments}

\begin{itemize}
    \item[1.] Officers may propose Amendments to Constitution. 
    \item[2.] Amendments shall be approved by two-thirds of the Board of Officers,
    \item[3.] The President or Vice-President may veto any proposed Amendments to this 
    Constitution 
\end{itemize}

\newpage

\begin{center}
    This Constitution has been formally approved by the membership of the organization \\
    \vspace{10pt}
    \textbf{Authorized representative:} Anders Poirel, President \\
    \vspace{10pt}
    \textbf{Date:} October $23^{rd}$, 2020
\end{center}

\end{document}